Verifying Demonstrations

### 2018-11-30 paper/privacy-properties.tex
harmonization, pass 2 (still WIP)

For privacy, any temporary identifiers, such as pseudonyms, should only be 
reused when strictly necessary (by the principle of data minimization) for the 
fulfillment of verifiability properties (in \cref{verifiability-properties}) to 
prevent inference on long-term identities by repeated samples and side 
information.
We can thus summarize the desired privacy properties as follows:
\begin{requirements}[P]
\item\label{PseudonymUnlink} \emph{Pseudonym unlinkability}: given a protest 
  (identifier \cid), protesters Alice and Bob, and a pseudonym \(\pid_b\), the 
  adversary cannot tell if \(\pid_b = \pid_{\text{Alice}}\) or \(\pid_b = 
    \pid_{\text{Bob}}\), except with negligible probability.
\item\label{ProtestUnlink} \emph{Protest unlinkability}: protesters' pseudonyms 
  (\(\pid_\cid, \pid_{\cid'}\)) must be unlinkable between protests (\(\cid, 
    \cid'\)) from the adversary's perspective.
\item\label{WitnessUnlink}\emph{Witness unlinkability}:  witnesses' pseudonyms 
  (\(\wid_\pid, \wid_{\pid'}\)) must be unlinkable between protesters (\(\pid, 
    \pid'\)) from the adversary's perspective.
\end{requirements}

What these properties say is that pseudonyms must look random 
(\cref{PseudonymUnlink}) and that each pseudonym must be used at most once 
(\cref{ProtestUnlink,WitnessUnlink}).

>>>>

For privacy, any temporary identifiers, such as pseudonyms, should only be 
reused when strictly necessary (by the principle of data minimization) for the 
fulfillment of verifiability properties (in \cref{verifiability-properties}) to 
prevent inference on long-term identities by repeated samples and side 
information.
We can thus summarize the desired privacy properties as follows:
\begin{requirements}[P]
\item\label{PseudonymUnlink} \emph{Pseudonym unlinkability}: given a protest 
  (identifier \cid), protesters Alice and Bob, and a pseudonym \(\pid_b\), the 
  adversary cannot tell if \(\pid_b = \pid_{\text{Alice}}\) or \(\pid_b = 
    \pid_{\text{Bob}}\), except with negligible probability. And similarly with $wid$ if Alice and Bob act as witnesses.
\item\label{ProtestUnlink} \emph{Protest unlinkability}: protesters' pseudonyms 
  (\(\pid_\cid, \pid_{\cid'}\)) must be unlinkable between protests (\(\cid, 
    \cid'\)) from the adversary's perspective.
\item\label{WitnessUnlink}\emph{Witness unlinkability}:  witnesses' pseudonyms 
  (\(\wid_\pid, \wid_{\pid'}\)) must be unlinkable between protesters (\(\pid, 
    \pid'\)) from the adversary's perspective.
\end{requirements}

What these properties say is that pseudonyms must look random 
(\cref{PseudonymUnlink}) and that each pseudonym must be used as little as possible to still ensure the verifiability properties defined in the previous subsection
(\cref{ProtestUnlink,WitnessUnlink}).

### 2018-11-30 paper/protest-model.tex
shortens some titles, integrates protocol overview in text, removes keywords etc. turns paragraphs into subsections for correct numbering
harmonization, pass 2 (still WIP)

\emph{Formalizing the notion of crowd estimation.} 
Each participant who wants to be counted must submit a \emph{participation proof}.
The proof must be associated with the protest (\ie its cause identifier \(cid\)), and its time and location must coincide with one of the subprotests.

Our protocol relies on \emph{witnesses} to certify and associate the proof to the time and location by creating a \emph{proof share}.
A witness is only allowed to create one proof share per protester to avoid the risk of count inflation.
(Note that a participant of a protest can take the role of a protester but also 
act as witness for other protesters.)
Then, the set of all \emph{eligible} proof shares forms the participation proof of a protester.

@@

\begin{definition}[Eligible proof share]%
  \label{DefProofShare}\label{DefProofShares}
  A \emph{proof share} \(\psh = (\cid, t, l, \pid, \wid)\) is a tuple in which: 
  \(\cid, t, l\) are as in \cref{DefProtest};
  \(\pid\) is a protester's pseudonym for the protest identified by \(\cid\); and \(\wid\) is a witness's pseudonym for a protester with pseudonym \(\pid\).\\
  Furthermore, we say that \(\psh\) is \emph{eligible} for a subprotest \(\sprtst = (\cid', t', l')\) if and only if \(\cid = \cid', t\subseteq t', l\subseteq l'\) and denote this by 
  \(\psh \sqsubseteq \sprtst\).

@@

% proof
% proofs
\begin{definition}[Participation proof]%
  \label{DefParticipationProof}\label{DefParticipationProofs}
  The \emph{participation proof} of a protester with pseudonym \(\pid\) who participates in a protest \(\prtst\) with cause identifier \(\cid\) is the 
  set
  \begin{equation}
    \nonumber
    \prf_{\pid, \prtst} =
    \left\{ \psh \in \pshs_{\cid, \pid} \mid
      \exists \sprtst\in \prtst\colon \psh\sqsubseteq \sprtst \right\},
  \end{equation}
  of all proof shares with the same protester and protest identifiers, and eligible for any subprotest $p$ of $\prtst$.
  We denote by \(\prfs\) the set of all proofs.
\end{definition}

@@

We can now define the participation count as follows.
\begin{definition}[Participation count]%
  \label{DefParticipationCount}
  We define a \emph{participation count} of a protest \(\prtst\) as the cardinality 
  \(|\prfs_{\prtst}^{\str,\theta}|\) of the set of \emph{valid} participation proofs respectively to a strength function $\str$ and a threshold $\theta$: \[
    \prfs_{\prtst}^{\str,\theta} = \left\{ \prf_{i,\prtst} \in \prfs \mid
      \str(\prf_{i,\prtst})\geq \theta \right\}
  \] with \(\str\colon \powerset(\pshs)\to \RR_+\) and  \(\theta \in \RR_+\).
\end{definition}

The strength function \(\str\) can be used to regulate the trust in the 
participation count estimated. In general, \(\str\) can be defined as a 
weighted sum of the proof shares, \(\str = \sum \omega_i s_i\), with the 
weights \(\omega_i\) being the trust in the witness corresponding to that proof 
share \(s_i\), and the threshold \(\theta\) representing the total trust needed 
to accept a participant as valid.
One example would be to set all weights to 1 for \(\str\) to return the number of unique witnesses and thus let \(\theta\) be the number of required witnesses.
Another possibility would be to also have a particular type of witness, called \emph{trusted witness}, participating in the protest. 
For instance, the role of the trusted witness could be taken by Jane, the independent journalist. 
In this situation, the weights would be 1 for trusted witnesses and 0 for any other witness, and
setting \(\theta = 1\) would require at least one proof share issued by a trusted witness.
Finally, both approaches can be combined by giving a weight of 1 to all 
non-trusted witnesses and a weight of \(\theta\) to trusted witnesses. This 
results in a participant being valid if they are witnessed either by \(\theta\) 
non-trusted witness or by one trusted witness.

>>>>

%\emph{Formalizing the notion of crowd estimation.} 
Each participant who wants to be counted must submit a \emph{participation proof}.
The proof must be associated with the protest (\ie its cause identifier \(cid\)), and its time and location must coincide with one of the subprotests.

Our protocol relies on \emph{witnesses} to certify and associate the proof to the time and location by creating a \emph{proof share}.
A witness is only allowed to create one proof share per protester to avoid the risk of count inflation.
(Note that a participant of a protest can take the role of a protester but also 
act as witness for other protesters.)
Then, the set of all \emph{valid} proof shares forms the participation proof of a protester.

@@

\begin{definition}[Valid proof share]%
  \label{DefProofShare}\label{DefProofShares}
  A \emph{proof share} \(\psh = (\cid, t, l, \pid, \wid)\) is a tuple in which: 
  \(\cid, t, l\) are as in \cref{DefProtest};
  \(\pid\) is a protester's pseudonym for the protest identified by \(\cid\); and \(\wid\) is a witness's pseudonym for a protester with pseudonym \(\pid\).\\
  Furthermore, we say that \(\psh\) is \emph{valid} for a subprotest \(\sprtst = (\cid', t', l')\) if and only if \(\cid = \cid', t\subseteq t', l\subseteq l'\) and denote this by 
  \(\psh \sqsubseteq \sprtst\).

@@

% proof
% proofs
\begin{definition}[Participation proof]%
  \label{DefParticipationProof}\label{DefParticipationProofs}
  The \emph{participation proof} of a protester with pseudonym \(\pid\) who participates in a protest \(\prtst\) with cause identifier \(\cid\) is the 
  set
  \begin{equation}
    \nonumber
    \prf_{\pid, \prtst} =
    \left\{ \psh \in \pshs_{\cid, \pid} \mid
      \exists \sprtst\in \prtst\colon \psh\sqsubseteq \sprtst \right\},
  \end{equation}
  of all proof shares with the same protester and protest identifiers, and valid for any subprotest $p$ of $\prtst$.
  We denote by \(\prfs\) the set of all proofs.
\end{definition}

@@

We can now define the participation count as follows.
\begin{definition}[Participation count]%
  \label{DefParticipationCount}
  We define a \emph{participation count} of a protest \(\prtst\) as the cardinality 
  \(|\prfs_{\prtst}^{\str,\theta}|\) of the set of \emph{eligible} participation proofs respectively to a strength function $\str$ and a threshold $\theta$: \[
    \prfs_{\prtst}^{\str,\theta} = \left\{ \prf_{i,\prtst} \in \prfs \mid
      \str(\prf_{i,\prtst})\geq \theta \right\}
  \] with \(\str\colon \powerset(\pshs)\to \RR_+\) and  \(\theta \in \RR_+\).
\end{definition}

The strength function \(\str\) can be used to regulate the trust in the 
participation count estimated. In general, \(\str\) can be defined as a 
weighted sum of the proof shares, \(\str = \sum \omega_i s_i\), with the 
weights \(\omega_i\) being the trust in the witness corresponding to that proof 
share \(s_i\), and the threshold \(\theta\) representing the total trust needed 
to accept a participant as eligible.
One example would be to set all weights to 1 for \(\str\) to return the number of unique witnesses and thus let \(\theta\) be the number of required witnesses.
Another possibility would be to also have a particular type of witness, called \emph{trusted witness}, participating in the protest. 
For instance, the role of the trusted witness could be taken by Jane, the independent journalist. 
In this situation, the weights would be 1 for trusted witnesses and 0 for any other witness, and
setting \(\theta = 1\) would require at least one proof share issued by a trusted witness.
Finally, both approaches can be combined by giving a weight of 1 to all 
non-trusted witnesses and a weight of \(\theta\) to trusted witnesses. This 
results in a participant being eligible if they are witnessed either by \(\theta\) 
non-trusted witness or by one trusted witness.

### 2018-11-30 paper/protocol.tex
harmonization, pass 2 (still WIP)

We now present \CROCUS, a protocol for privately verifyiable crowd counts.
The protocol consists of five phases: setup (in \cref{ProtocolSetup}),
join, participation, submission (all in in \cref{ProtocolDuring}) and
verification (in \cref{ProtocolVerification}).

Several entities are involved in our protocol.
First, \iac{CA} is responsible for certifying a one-to-one mapping between a 
person's identity and a cryptographic key\footnote{%
  This can be done by a centralized authority, such as a nation state with, 
  \eg, passports; or a decentralized authority, as in the case of a a 
  collective authority~\cite{collective-signing} powered by 
  proof-of-personhood~\cite{proof-of-personhood}.
}.
The \ac{CA} is only involved in the setup phase.
Second, a participant is an individual who wants to participate in a given 
protest.
A participant can assume three different roles:
\begin{enumerate}
\item The \emph{organizer} has written a manifesto for the protest and forward it to others.
\item A \emph{protester} is attending the protest and asks witnesses to vouch 
  for his presence.
\item A \emph{witness} provides proofs to protesters which state that the 
  protester was indeed participating and such that the proofs are verifiable by 
  third parties.
\end{enumerate}
In general, there is one organizer and every participant can act alternatively 
as both protester and witness.

\subsection{Setup phase}%
\label{ProtocolSetup}

The setup phase is only run once and is the same as in Anon-Pass~\cite{AnonPass}.
More precisely, we have simply adapted their description to our notation, but otherwise we have the setting as similar as possible.

\emph{Setup: \((\spk, \ssk)\gets \CROCUSsetup\).}
During the setup phase, the \ac{CA} creates all the needed keys.
The \ac{CA} generates a service public-private key-pair \((\spk, \ssk)\gets 
  \ACsetup\) (see \cref{CLsignAlg}).

\emph{Registration: \(\sk\gets 
    \Proto{\CROCUSreg[_P][\spk]}{\CROCUSreg[_{\CA}][\ssk]}\).}
During the registration phase, each participant generates a secret key and 
obtains a signature on it by the \ac{CA} but without revealing it to the 
\ac{CA}.
At the end, each participant will have a signed secret key while the \ac{CA} 
will issue only one signature per participant but without knowing the 
association between a particular key and the identity of the participant.
The participant chooses \(k, r\rgets \ZZ_q\) uniformly randomly and runs 
\(\sigma \gets \Proto{\ACgetSig[\spk, k, r]}{\ACissueSig[\spk, \ssk]}\) (see 
\cref{CLacSigAlg}).
Upon success, the participant sets \(\sk = (\sigma, k, r)\).

The setup and registration phases can be done once and the keys can be reused 
for an arbitrary number of protests.
Thus, the registration phase could be easily integrated as part of the issuance 
of national identity cards, passports or \acp{eID}.

\subsection{Creation, join and participation in a protest and submission of proofs}%
\label{ProtocolDuring}

The join, participation and submission phases are illustrated in \cref{fig:ProtocolOverview}.
The participation proof share that will be constructed in the participation phase is illustrated in \cref{fig:ProofFig}.

@@

\begin{figure}
  \centering
  \small
  \begin{minipage}{\linewidth}
    \begin{align*}
      O\to \text{all}\colon & \text{manifesto} \\
      P\colon & t_s\gets \TSget \\
        & \cid\gets \Hash[\text{manifesto}], \\
        & \pid\gets \ACprf[_{\sk_P}][\cid] \\
      W\colon & t_s'\gets \TSget
      \\[-1em]
      \noalign{\hfill Join}
      \midrule
      \noalign{\hfill Participation}
      \\[-3em]
      P\to W\colon & \pid \\
      P\leftrightarrow W\colon &
        \PPK\mleft\{ (\sk_P) : \mright. \\
        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
        \\
      W\colon & \wid\gets \ACprf[_{\sk_W}][\pid] \\
      W\to P\colon & (\wid, t_s', l)
      \\[-1em]
      \noalign{\hfill Participation}
      \midrule
      \noalign{\hfill Submission}
      \\[-2em]
      P\colon & t_e\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
      W\colon & t_e'\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
      W\to S\colon & (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\wid}),\quad 
      \text{where} \\
        & \pi_{\wid} = \SPK\mleft\{ (\sk_W) : \mright. \\
        & \qquad \wid = \ACprf[_{\sk_W}][\pid], \\
        & \qquad \mleft. \sigma_W' = \ACblind[\ACsign[_{\ssk}][\sk_W]]\mright\} 
        \\
        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l) \\
      P\to S\colon & (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\pid}),\quad 
      \text{where}\\
        & \pi_{\pid} = \SPK\mleft\{ (\sk_P) : \mright. \\
        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
        \\
        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l)
    \end{align*}
  \end{minipage}
  \caption{%
    An overview of the Join, Participation and Submission phases of \CROCUS.\@
    The organizer \(O\) broadcasts the manifesto.
    The protester \(P\), witness \(W\) and their computations are as in \cref{fig:ProofFig}.
    Finally, both \(P\) and \(W\) submit the proof shares to a
    permanent storage \(S\). Note that \pid always refers to the
    protester whose presence is being witnessed.
  }%
  \label{fig:ProtocolOverview}
\end{figure}

@@

\emph{Participation: \(\pi\gets
    \Proto{\CROCUSparticipate[\cid, \sk_P]}{\CROCUSwitness[\sk_W, \spk]}\),}
In the participation phase (see \cref{fig:ProtocolOverview}), the protester and 
the witness construct the proof share of the protester (\cref{fig:ProofFig}).

The protester sends \(\pid\) to the witness.
Then they run the protocol \(\Proto{\ACproveSig[\spk, k, r, 
    \sigma]}{\ACverifySig[\spk, \ssk]}\) (see \cref{ACacAlg}).
Note that the \ac{PK} in \cref{ACacAlg} must be run as \iac{PPK}.
If the protocol succeeds, the witness will compute \(\wid \gets 
  \ACprf[_{\sk_W}][\pid]\) and send \((\wid, t_s', l)\) to the protester.

\emph{Submission: \(\psh_P\gets \CROCUSsubmit[_P][\cid, \pid, \wid, t_s, t_s',  l]\).}
The participant should as soon as possible commit the proof-share data to the 
time-stamping service and receive the proof of commitment, \(t_e\gets 
  \TSstamp[\Hash[\cid, \pid, \wid, t_s, t_s', l]]\).
The remaining operations are not time critical.

@@

\emph{Submission: \(\psh_W\gets \CROCUSsubmit[_W][\cid, \pid, \wid, t_s, t_s', 
    l]\).}
The witness should, just as the participant, commit the proof-share data to the 
time-stamping service, \(t_e'\gets \TSstamp[\Hash[\cid, \pid, \wid, t_s, t_s', 
  l]]\).
(This is to make the time interval as early as possible, whoever is the faster 
will submit it.)
Then, without any time requirements, the witness computes \iac{NIZK} proof 
\(\corr_{\wid}\) as follows:
\begin{multline*}
  \corr_{\wid}\gets \SPK\left\{ (\sk_W) : \right. \\
    \begin{aligned}
      \wid &= \ACprf[_{\sk_W}][\pid] \quad \land \\
      \sigma_W' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_W]] \right\}
    \end{aligned} \\
      (\cid, \pid, \wid, t_s, t_s', l).
\end{multline*}
Finally, the witness uploads the tuple \[
  \psh_W = (\cid, \pid, \wid, t_s, t_s', t_e', l, \corr_{\wid})
\] for permanent storage.

\subsection{Verifying the participation count}%
\label{ProtocolVerification}

@@

To verify the participation count for a subprotest \(\sprtst = (\cid, t, l)\) 
(see \cref{DefProtest}), a verifier must download all the proof shares \[
  \psh_i =   (\cid, \pid_j, \wid_i, t_s^{(i)}, t_s^{\prime (i)}, t_e^{(i)}, 
  t_e^{\prime   (i)}, l_i, \corr_{\pid_j}^{(i)}, \corr_{\wid_i})
\] for each protester \(j\) from the ledger, verify \(\corr_{\pid_j}^{(i)}\), 
\(\corr_{\wid_i}\) and that the interval \(\interval{\max(t_s^{(i)}, 
    t_s^{\prime (i)})}{\min(t_e^{(i)}, t_e^{\prime (i)})}\subseteq t\) and that 
\(l_i\subseteq  l\).
Any proof share that does not verify correctly will be discarded.
At this point, the verifier has constructed the set \(S\) from 
\cref{DefProofShares} and can thus construct any participation proof 
\(\prf_{\pid_j, P}\) as in \cref{DefParticipationProof}.
Now the verifier can compute the participation count \(|\prfs_P^{\str, 
    \theta}|\) as in \cref{DefParticipationCount}.

>>>>

We now present \CROCUS, a protocol for privately verifiable crowd counts.
The protocol consists of three phases:
before the protest, with the setup and registration steps (\cref{ProtocolSetup}),
during the protest, with the creation, join, participation, and submission steps (\cref{ProtocolDuring})
and after the protest, with the verification step (in \cref{ProtocolVerification}).

Several entities are involved in our protocol.
First, a \emph{certificate authority} (\ac{CA}) is responsible for certifying a one-to-one mapping between a 
person's identity and a cryptographic key\footnote{%
  This can be done by a centralized authority, such as a nation state with, 
  \eg, passports; or a decentralized authority, as in the case of a a 
  collective authority~\cite{collective-signing} powered by 
  proof-of-personhood~\cite{proof-of-personhood}.
}.
The \ac{CA} is only involved in the setup phase.
Second, a participant is an individual who wants to participate in a given 
protest.
A participant can assume three different roles:
\begin{enumerate}
\item The \emph{organizer} has written a manifesto for the protest and forwards it to others.
\item A \emph{protester} is attending the protest and asks witnesses to vouch 
  for his presence.
\item A \emph{witness} provides proofs to protesters which state that the 
  protester was indeed participating and such that the proofs are verifiable by 
  third parties.
\end{enumerate}
In general, there is one organizer and every participant can act alternatively 
as both protester and witness.

\subsection{Pre-protest phase}%
\label{ProtocolSetup}

The setup step is only run once and is the same as in Anon-Pass~\cite{AnonPass}.
More precisely, we have simply adapted their description to our notation, but otherwise kept the setting as similar as possible.

\emph{Setup: \((\spk, \ssk)\gets \CROCUSsetup\).}
During the setup step, the \ac{CA} creates all the needed keys.
First, the \ac{CA} generates a service public-private key-pair \((\spk, \ssk)\) as follows.
Let \(G = \gen g\) be a group with generator \(g\) and of prime order \(q\).
Let \(G_T\) be a group such that there is a bilinear pairing \(e\colon G\times G\to G_T\)\footnote{%
  \Ie \(e(g_1^a, g_2^b) = e(g_1, g_2)^{ab}\) and if \(G = \gen{g_1} = 
    \gen{g_2}\) then \(G_T = \gen{e(g_1, g_2)}\).
}.
Choose \(x,y,z\rgets \ZZ_q\) uniformly at random and set \(X = g^x, Y = g^y, Z = g^z\).
The service public key is set to \(\spk = (q, G, G_T, g, X, Y, Z)\) and the service private key to \(\ssk = (x, y, z)\).

\emph{Registration: \(\sk\gets 
    \Proto{\CROCUSreg[_P][\spk]}{\CROCUSreg[_{\CA}][\ssk]}\).}
During the registration step, each participant generates a secret key and 
obtains a signature on it by the \ac{CA} but without revealing it to the 
\ac{CA}.
At the end, each participant will have a signed secret key while the \ac{CA} 
will issue only one signature per participant but without knowing the 
association between a particular key and the identity of the participant.
The participant chooses \(k, r\rgets \ZZ_q\) uniformly randomly, sets \(M = g^k Z^r\) and sends \(M\) to the server.
The participant acts as prover and the \ac{CA} as verifier while they perform 
the following \ac{ZKPK} protocol:
\[
  \PK[k,r][M = g^k Z^r].
\]
If the proof succeeds, the \ac{CA} chooses \(a\rgets \ZZ_q^*\) and sets \(A = g^a\).
Afterwards, he forms the signature \(\sigma = (A, B = A^y, Z_B = B^z = Z^{ay}, 
  C = A^x M^{axy})\) and sends it to the participant.
The participant then verifies that the following equations hold:
\begin{align*}
  A &\neq 1 \\
  e(g, B) &= e(Y, A) \\
  e(g, Z_B) &= e(Z, B) \\
  e(g, C) &= e(X, A) e(X, B)^k e(X, Z_B)^r.
\end{align*}
Upon success, the participant sets \(\sk = (\sigma, k, r)\).

The setup and registration steps can be done once and the keys can be reused 
for an arbitrary number of protests.
Thus, the registration step could be easily integrated as part of the issuance 
of national identity cards, passports or \acp{eID}.

\subsection{Protest phase}%
\label{ProtocolDuring}

The join, participation and submission steps are illustrated in \cref{fig:ProtocolOverview}.
The participation proof share that will be constructed in the participation step is illustrated in \cref{fig:ProofFig}.

@@

\begin{figure}
  \centering
  \small
  \begin{minipage}{\linewidth}
    \begin{align*}
      O\to \text{all}\colon & \text{manifesto} \\
      P\colon & t_s\gets \TSget \\
        & \cid\gets \Hash[\text{manifesto}], \\
        & \pid\gets \ACprf[_{\sk_P}][\cid] \\
      W\colon & t_s'\gets \TSget
      \\[-1em]
      \noalign{\hfill Join}
      \midrule
      \noalign{\hfill Participation}
      \\[-3em]
      P\to W\colon & \pid \\
      P\leftrightarrow W\colon &
        \PPK\mleft\{ (\sk_P) : \mright. \\
        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
        \\
      W\colon & \wid\gets \ACprf[_{\sk_W}][\pid] \\
      W\to P\colon & (\wid, t_s', l)
      \\[-1em]
      \noalign{\hfill Participation}
      \midrule
      \noalign{\hfill Submission}
      \\[-2em]
      P\colon & t_e\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
      W\colon & t_e'\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
      W\to S\colon & (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\wid}),\quad 
      \text{where} \\
        & \pi_{\wid} = \SPK\mleft\{ (\sk_W) : \mright. \\
        & \qquad \wid = \ACprf[_{\sk_W}][\pid], \\
        & \qquad \mleft. \sigma_W' = \ACblind[\ACsign[_{\ssk}][\sk_W]]\mright\} 
        \\
        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l) \\
      P\to S\colon & (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\pid}),\quad 
      \text{where}\\
        & \pi_{\pid} = \SPK\mleft\{ (\sk_P) : \mright. \\
        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
        \\
        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l)
    \end{align*}
  \end{minipage}
  \caption{%
    An overview of the Join, Participation and Submission phases of \CROCUS.\@
    The organizer \(O\) broadcasts the manifesto.
    The protester \(P\), witness \(W\) and their computations are as in \cref{fig:ProofFig}.
    Finally, both \(P\) and \(W\) submit the proof shares to a
    permanent storage \(S\). Note that \pid{} always refers to the
    protester whose presence is being witnessed.
  }%
  \label{fig:ProtocolOverview}
\end{figure}

@@

\emph{Participation: \(\pi\gets
    \Proto{\CROCUSparticipate[\cid, \sk_P]}{\CROCUSwitness[\sk_W, \spk]}\),}
In the participation phase, the protester and the witness construct the proof share of the protester (\cref{fig:ProofFig}).
The protester blinds his signature \(\sigma\) on his secret key by choosing \(r_1, r_2\rgets \ZZ_q^*\) and generates \(
  \tilde\sigma = (\tilde A = A^{r_1},
                  \tilde B = B^{r_1},
                  \tilde Z_B = Z_B^{r_1},
                  \hat C = C^{r_1 r_2}).
\) 
Note that it is not necessary to compute a new \(\tilde\sigma\) more than once per \(\pid\).
The protester sends \((\pid, \tilde\sigma)\) to the witness.
The witness verifies that
\begin{align*}
  \tilde A          &\neq 1 \\
  e(g, \tilde B)    &= e(Y, \tilde A) \\
  e(g, \tilde Z_B)  &= e(Z, \tilde B).
\end{align*}
Both the protester and the witness compute
\begin{align*}
  v &= e(g, \hat C) \\
  v_x &= e(X, \tilde A) \\
  v_{xy} &= e(X, \tilde B) \\
  v_{xy}' &= e(X, \tilde Z_B).
\end{align*}
Afterwards, they run the following \ac{PPK} with the protester as the prover 
and the witness as the verifier:
\begin{multline*}
  \mleftright
  \PPK\left\{(k, r, r') : v^{r'} = v_x v_{xy}^k v_{xy}^{\prime r} \land
    \pid = g_T^{1/(k_P+\cid)} \right\}.
\end{multline*}
in which \(r' = 1/r_2\).
We can rewrite \(\pid = g_T^{1/(k+\cid)}\) as \(\pid^k = g_T g_T^{-\cid}\).
Afterwards, the \ac{PK} can be designed as follows.
(Remember that this \ac{PK} should be run as the \ac{PPK} in 
\cref{DB-anon-cred} and repeated multiple times to achieve security.)
The protester chooses \(r_k, r_r, r_{r'}\rgets \ZZ_q\) uniformly at random, 
sets \(R_1 = v^{r_{r'}} v_{xy}^{r_k} v_{xy}^{\prime r_r}\) and \(R_2 = 
  \pid^{r_k}\) and sends \(R_1, R_2\) to the witness.
The witness replies with a challenge \(c\).
Afterwards, the protester computes
\begin{align*}
  s_k &= -ck + r_k, \\
  s_r &= -cr + r_r, \\
  s_{r'} &= cr' + r_{r'}
\end{align*}
and forwards them to the witness.
The witness checks whether
\begin{align*}
  v_x^c R_1 &\overset{\mathclap{?}}{=} v^{s_{r'}} v_{xy}^{s_k} v_{xy}^{\prime 
    s_r}, \\
  \mleft(g_T \pid^{-\cid}\mright)^{-c} R_2 &\overset{\mathclap{?}}{=} 
  \pid^{s_k}.
\end{align*}
If the proof succeeds, the witness computes \(\wid\gets \ACprf[_{\sk_W}][\pid] 
  = g_T^{1/(k_W+\pid)}\) (as above).
Following this, the witness returns \((\wid, t_s', l)\) to the protester.
As a consequence, both the protester and the witness have the tuple \(\psh = 
  (\cid, \pid, \wid, t_s, t_s', l)\), which forms a proof share for the 
protester (\cref{fig:ProofFig}).

\emph{Submission: \(\psh_P\gets \CROCUSsubmit[_P][\cid, \pid, \wid, t_s, t_s',  l]\).}
The protester should as soon as possible commit the proof-share data to the 
time-stamping service and receive the proof of commitment, \(t_e\gets 
  \TSstamp[\Hash[\cid, \pid, \wid, t_s, t_s', l]]\).
The remaining operations are not time critical.

@@

\emph{Submission: \(\psh_W\gets \CROCUSsubmit[_W][\cid, \pid, \wid, t_s, t_s', 
    l]\).}
The witness should, just as the protester, commit the proof-share data to the 
time-stamping service, \(t_e'\gets \TSstamp[\Hash[\cid, \pid, \wid, t_s, t_s', 
  l]]\).
(This is to make the time interval as early as possible, whoever is the faster 
will submit it.)
Then, without any time requirements, the witness computes \iac{NIZK} proof 
\(\corr_{\wid}\) as follows:
\begin{multline*}
  \corr_{\wid}\gets \SPK\left\{ (\sk_W) : \right. \\
    \begin{aligned}
      \wid &= \ACprf[_{\sk_W}][\pid] \quad \land \\
      \sigma_W' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_W]] \right\}
    \end{aligned} \\
      (\cid, \pid, \wid, t_s, t_s', l).
\end{multline*}
Finally, the witness uploads the tuple \[
  \psh_W = (\cid, \pid, \wid, t_s, t_s', t_e', l, \corr_{\wid})
\] for permanent storage.

\subsection{Post-protest phase}%
\label{ProtocolVerification}

@@

To verify the participation count for a protest \(\prtst\)  with identifier $\cid$
(see \cref{DefProtest}), a verifier must download all the proof shares \[
  \psh_i =   (\cid, \pid_j, \wid_i, t_s^{(i)}, t_s^{\prime (i)}, t_e^{(i)}, 
  t_e^{\prime   (i)}, l_i, \corr_{\pid_j}^{(i)}, \corr_{\wid_i})
\] for each protester \(j\) from the ledger, verify \(\corr_{\pid_j}^{(i)}\), 
\(\corr_{\wid_i}\) and that the interval \(\interval{\max(t_s^{(i)}, 
    t_s^{\prime (i)})}{\min(t_e^{(i)}, t_e^{\prime (i)})}\subseteq t\) and that 
\(l_i\subseteq  l\).
Any proof share that does not verify correctly will be discarded.
At this point, the verifier has constructed the set \(S\) from 
\cref{DefProofShares} and can thus construct any participation proof 
\(\prf_{\pid_j, P}\) as in \cref{DefParticipationProof}.
Now the verifier can compute the participation count \(|\prfs_P^{\str, 
    \theta}|\) as in \cref{DefParticipationCount}.

### 2018-11-30 paper/timestamp.tex
Changes equality to inequality for timestamp comparison
shortens some titles, integrates protocol overview in text, removes keywords etc. turns paragraphs into subsections for correct numbering
harmonization, pass 2 (still WIP)

\subsection{Time-stamping service -- distributed ledger}%
\label{StorageProperties}

We need a robust time-stamping service, \(\TS\), which implements the \(\TSget\), \(\TSstamp\) and \(\TStime\) requests such that
\begin{itemize}
  \item \(\rho \gets \TSget\) yields a value \(\rho\) at time \(t\), \(\rho\) is difficult to guess before time \(t\) and \(\TStime[\rho] = t\);
  \item \(\pi\gets \TSstamp[x]\) yields a value \(\pi\) at time \(t\) such that \(\TSverify[x, \pi]\to \top\) and \(\TStime[\pi] = t\).
\end{itemize}

@@

The tuple \((\rho_{t_0}, m, \pi_{t_1})\) can be used to prove that \(m\) was created within the time interval \(\interval{t_0}{t_1}\).
The verifier computes \(h'\gets \Hash[m, \rho_{t_0}]\) and checks whether \(\TSverify[h', \pi_{t_1}] = \top\) and \(\TStime[\rho_{t_0}] = t_0\land 
  \TStime[\pi_{t_1}] = t_1\).

>>>>

\subsection{Time-stamping and storage --- distributed ledger}%
\label{StorageProperties}\label{timestamp}\label{ledger}

We need a robust time-stamping service, \(\TS\), which implements the \(\TSget\), \(\TSstamp\) and \(\TStime\) requests such that
\simon{"request" feels weird to me. Are we sure that's the right word?}
\begin{itemize}
  \item \(\rho \gets \TSget\) yields a value \(\rho\) at time \(t\), \(\rho\) is difficult to guess before time \(t\) and \(\TStime[\rho] = t\);
  \item \(\pi\gets \TSstamp[x]\) yields a value \(\pi\) at time \(t\) such that \(\TSverify[x, \pi]\to \top\) and \(\TStime[\pi] = t\).
\end{itemize}

@@

The tuple \((\rho_{t_0}, m, \pi_{t_1})\) can be used to prove that \(m\) was created within the time interval \(\interval{t_0}{t_1}\).
The verifier computes \(h'\gets \Hash[m, \rho_{t_0}]\) and checks whether \(\TSverify[h', \pi_{t_1}] = \top \land \TStime[\rho_{t_0}] = t_0\land 
  \TStime[\pi_{t_1}] = t_1\).
